Open Data, Open Source and Open Standards in chemistry - The Blue Obelisk five years on

### 2011-04-15 paper.tex
Minor fix to heading
Fix column width to 70. I have learned the magic of 'set textwidth=70' in vim.

\subsection*{Cheminformatics toolkits}

@@

Bioclipse \cite{Bioclipse2} (v1.0 released in Aug 2006) and Avogadro
\cite{WebAvogadro} (v1.0 in Oct 2009) are two examples of such software, based on the CDK and Open Babel, respectively. Bioclipse is an award-winning `molecular workbench' for life sciences that ..., while Avogadro is a 3D molecular editor and viewer aimed at preparing and analysis computational chemistry calculations. An interesting aspect of both of these projects is that they share some developers with the underlying toolkit and this has driven the development of new features in the CDK and Open Babel (??? is this true for the CDK too? ???).

@@

Although the software developed by the Blue Obelisk is Open Source on principle, this does not rule out the establishment of a business based on open source chemistry software. Rather than supporting itself through sales, such a business generally relies on providing support, customisation and services around the software. The interaction between an open source project and a company is important, and works best where there is some form of `giving back' to the project (such as developer time, code contributions, or finanical assistance with server costs).

>>>>

\subsubsection*{Cheminformatics toolkits}

@@

Bioclipse \cite{Bioclipse2} (v1.0 released in Aug 2006) and Avogadro
\cite{WebAvogadro} (v1.0 in Oct 2009) are two examples of such
software, based on the CDK and Open Babel, respectively. Bioclipse is
an award-winning `molecular workbench' for life sciences that ...,
while Avogadro is a 3D molecular editor and viewer aimed at preparing
and analysing computational chemistry calculations. An interesting
aspect of both of these projects is that they share some developers
with the underlying toolkit and this has driven the development of new
features in the CDK and Open Babel.

@@

Although the software developed by the Blue Obelisk is Open Source on
principle, this does not rule out the establishment of a business
based on open source chemistry software. Rather than supporting itself
through sales, such a business generally relies on providing support,
customisation and services around the software. The interaction
between an open source project and a company is important, and works
best where there is some form of `giving back' to the project (such as
developer time, code contributions, or financial assistance with server costs).
